
```{r}
library(pROC)
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyverse)

library(psych)
library(fastDummies)
library(interactions)
library(carData)
library(Hmisc)
library(readxl) 
library(dplyr)
library(ggplot2)
library(readr)
library(ggpubr)
library(tidyverse)
library(corrplot)
library(cowplot)
library(qwraps2)
library(magrittr)
library(lsr)
library(tidyr)
library(rstatix)
library(olsrr)
library(caret)
library(phd)
library(arsenal)
library(openxlsx)
library(car)

```


```{r}
cat("\014") # clear screen
rm(list=ls()) %>% gc(verbose = FALSE)  # Clear workspace and free memory

#set working directory

#load document



b$ASD_TDC <- as.factor(b$ASD_TDC)
b$ASD_TDC <- factor(b$ASD_TDC, levels = c("TDC", "ASD"))

b$t1_sex <- as.factor(b$t1_sex)
b$Vineland_difference <- as.numeric(b$Vineland_difference)
b$average_head_circumference <- as.numeric(b$average_head_circumference)
b$t1_group <- as.factor(b$t1_group)
```

```{r}
b <- b %>%
  mutate(age_difference = (t2_age - t1_age)/30.417)

b <- b %>% mutate(AgeBin = case_when(t1_age_years >= 6  & t1_age_years < 15 ~ '6-15',
                                     t1_age_years >= 15  & t1_age_years < 25 ~ '15-24',
                                             t1_age_years >= 25  & t1_age_years <= 32 ~ '25-31')) 
         
b_nonID <- filter(b, ID_nonID == 'nonID')
ASD_nonID <- filter(b_nonID, t1_group == 'ASD')

#DEFINE VINELAND DATA

Vineland_data = filter(ASD_nonID, Vineland_difference != 'NA')

Vineland_data <- Vineland_data %>%
  arrange(t1_age_years)

#SCALING VARIABLES PRIOR TO HAVING THEM IN A GLM

# Define the list of predictors from your formula
Vineland_data$age_for_filtering <- Vineland_data$t1_age_years

predictors <- c(
  "PLV_6_9_DK_mean_SWI", "t1_fsiq",
                "PLV_6_9_DK_mean_mean_degree",
                "t1_vabsabcabc_standard", "t1_age_years","t1_age",
                "age_difference")

# Scale only the predictors
Vineland_data <- Vineland_data %>%
  mutate(across(all_of(predictors), ~ as.numeric(scale(.))))

#AGE GROUPS
Vineland_data_young = filter(Vineland_data, AgeBin == '6-15')
Vineland_data_middle =filter(Vineland_data, AgeBin == '15-22')
Vineland_data_old = filter(Vineland_data, AgeBin == '22-31')


```


#all participants age group analysis
```{r}

predictors <- c(
  "PLV_6_9_DK_mean_SWI", "t1_fsiq",
                "PLV_6_9_DK_mean_mean_degree",
                "t1_vabsabcabc_standard", "t1_age_years",
                "age_difference")

# Scale only the predictors
b_nonID <- b_nonID %>%
  mutate(across(all_of(predictors), ~ as.numeric(scale(.))))

young_nonID <- filter(b_nonID, AgeBin == '6-15')
middle_nonID <- filter(b_nonID, AgeBin == '15-24')
old_nonID <- filter(b_nonID, AgeBin == '25-31')

```


#Best models for paper with age groups - 19/3/2024
```{r}
#MD
MD <- lm(scale(PLV_6_9_DK_mean_mean_degree) ~ ASD_TDC + t1_age_years + I(t1_age_years^2) + t1_site + t1_sex, data = young_nonID) #best model
summary(MD) 

MD <- lm(scale(PLV_6_9_DK_mean_mean_degree) ~ ASD_TDC + t1_age_years + t1_sex + t1_site, data = middle_nonID)
summary(MD) 

MD <- lm(scale(PLV_6_9_DK_mean_mean_degree) ~ ASD_TDC + t1_age_years + I(t1_age_years^2) + t1_site, data = old_nonID)
summary(MD) 

#SWI
MD <- lm(scale(PLV_6_9_DK_mean_SWI) ~ ASD_TDC + t1_age_years + I(t1_age_years^2) + t1_site, data = young_nonID)
summary(MD) 

MD <- lm(scale(PLV_6_9_DK_mean_SWI) ~ ASD_TDC + t1_age_years  + t1_site + t1_sex, data = middle_nonID)
summary(MD) 

MD <- lm(scale(PLV_6_9_DK_mean_SWI) ~ ASD_TDC, data = old_nonID)
summary(MD) 

```


#GRAPHS FOR PAPER - AGE VS GRAPH THEORY - group differences
```{r}

PLV_6_9_DK_mean_mean_degree_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + I(t1_age_years^2) + t1_site + t1_sex, data = young_nonID))

#YOUNG MD
number_matricies <- ggplot(young_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_mean_degree_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5, outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#MD middle
PLV_6_9_DK_mean_md_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + t1_sex + t1_site, data = middle_nonID))

number_matricies <- ggplot(middle_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_md_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5,outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#MD OLD
PLV_6_9_DK_mean_mean_degree_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + I(t1_age_years^2) + t1_site, data = old_nonID))

number_matricies <- ggplot(old_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_mean_degree_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5,outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#YOUNG SWI
PLV_6_9_DK_mean_SWI_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_age_years + I(t1_age_years^2) + t1_site, data = young_nonID))

number_matricies <- ggplot(young_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5,outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Small world index (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

# MIDDLE SWI
PLV_6_9_DK_mean_SWI_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_age_years + t1_site  + t1_sex , data = middle_nonID))

number_matricies <- ggplot(middle_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5,outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Small world index (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#SWI OLD
number_matricies <- ggplot(old_nonID, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5,outlier.shape = NA)+
  scale_color_manual(values=c("#0086EA","orange"))+
  labs(x="", y = "Small world index", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

```

#significant Vineland models - 18/04/2025
```{r}
m2 <- lm(Vineland_difference ~  PLV_6_9_DK_mean_SWI + t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_sex, data = Vineland_data_middle)
summary(m2) # best AIC
effectsize::eta_squared(car::Anova(m2, type = 2), partial = FALSE)

m2 <- lm(Vineland_difference ~  t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_sex, data = Vineland_data_middle)
summary(m2) # best AIC

m3 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference +t1_sex + t1_site, data = Vineland_data_middle)
summary(m3) # best AIC
effectsize::eta_squared(car::Anova(m3, type = 2), partial = FALSE)


m3 <- lm(Vineland_difference ~  t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference +t1_sex + t1_site, data = Vineland_data_middle)
summary(m3) # best AIC


```


#Best Vineland predictive models for paper - 29/3/24 - SWI - IQ INCLUDED IF NEEDED - ENSURE EVERYTHING IS SCALED
```{r}

#6-31 SWI
m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_SWI + t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_site, data = ASD_nonID)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

m1 <- lm(Vineland_difference ~ t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_site, data = ASD_nonID)
summary(m1) # best AIC

#6-14 SWI
m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_SWI + t1_vabsabcabc_standard + t1_age_years* age_difference, data = Vineland_data_young)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

#15-24 SWI
m1 <- lm(Vineland_difference ~  PLV_6_9_DK_mean_SWI + t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_sex, data = Vineland_data_middle)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

m1 <- lm(Vineland_difference ~  t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference + t1_sex, data = Vineland_data_middle)
summary(m1) # best AIC
```

#Best Vineland predictive models for paper - 29/3/24 - MD - IQ INCLUDED
```{r}
#MD 6-31
m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_fsiq + t1_vabsabcabc_standard +  t1_age_years*age_difference + t1_site, data = ASD_nonID)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

#MD 6-14
m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_vabsabcabc_standard +  t1_age_years+age_difference +t1_sex + t1_site, data = Vineland_data_young)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

#MD 15-24
m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference +t1_sex + t1_site, data = Vineland_data_middle)
summary(m1) # best AIC
effectsize::eta_squared(car::Anova(m1, type = 2), partial = FALSE)

m1 <- lm(Vineland_difference ~ t1_fsiq + t1_vabsabcabc_standard + t1_age_years*age_difference +t1_sex + t1_site, data = Vineland_data_middle)
summary(m1) # best AIC
```



#Figures SIGNIFICANT VINELAND PREDICTIVE MODELS - IQ
```{r}
md_mid_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site + t1_sex, data = Vineland_data_middle))
Vineland_diff_mid_resid <-resid(lm(Vineland_difference ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site + t1_sex, data = Vineland_data_middle))

MD_mid <- ggplot(Vineland_data_middle, aes(x = md_mid_resid, y = Vineland_diff_mid_resid)) + geom_point()+
  geom_smooth(method='lm', se = FALSE)+
  labs(title = "c) Relationship between mean degree and \n change in ABC scores in autistic 15-24-year-olds",
         x="Mean degree (residual)", y = "ΔABC score (residual)")+
  theme(aspect.ratio = 0.7, panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
MD_mid


SWI_mid_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_sex, data = Vineland_data_middle))
Vineland_diff_SWI_mid_resid <-resid(lm(Vineland_difference ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_sex, data = Vineland_data_middle))

SWI_mid <- ggplot(Vineland_data_middle, aes(x = SWI_mid_resid, y = Vineland_diff_SWI_mid_resid)) + geom_point()+
  geom_smooth(method='lm', se = FALSE)+
  labs(title = "d) Relationship between small-world index and \n change in ABC scores in autistic 15-24-year-olds",
         x="Small world index (residual)", y = "ΔABC score (residual)")+
  theme(aspect.ratio = 0.7, panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))

SWI_mid

SWI_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site, data = Vineland_data_scaled))
Vineland_diff_SWI_resid <-resid(lm(Vineland_difference ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site, data = Vineland_data_scaled))

SWI_all <- ggplot(Vineland_data_scaled, aes(x = SWI_resid, y = Vineland_diff_SWI_resid)) + geom_point()+
  geom_smooth(method='lm', se = FALSE)+
  labs(title = "b) Relationship between small-world index and \n change in ABC scores in autistic 6-31-year-olds",x="Small world index (residual)", y = "ΔABC score (residual)")+
  theme(aspect.ratio = 0.7, panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) 
SWI_all

#MD all
MD_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site, data = Vineland_data_scaled))
Vineland_diff_MD_resid <-resid(lm(Vineland_difference ~ t1_vabsabcabc_standard + t1_fsiq + t1_age*age_difference + t1_site, data = Vineland_data_scaled))

MD_all <- ggplot(Vineland_data_scaled, aes(x = MD_resid, y = Vineland_diff_MD_resid)) + geom_point()+
  geom_smooth(method='lm', se = FALSE)+
  labs(title = "a) Relationship between mean degree and \n change in ABC scores in autistic 6-31-year-olds",x="Mean degree (residual)", y = "ΔABC score (residual)")+
  theme(aspect.ratio = 0.7, panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) 
MD_all

```

#SCALING VARIABLES PRIOR TO GLM
```{r}
#start from b
b_nonID <- filter(b, ID_nonID == 'nonID')
ASD_nonID <- filter(b, t1_group == 'ASD')
Vineland_data = filter(ASD_nonID, Vineland_difference != 'NA')

# Define the list of predictors from your formula
Vineland_data$age_for_filtering <- Vineland_data$t1_age_years

predictors <- c(
  "PLV_6_9_DK_mean_SWI", "t1_fsiq", 
                "PLV_6_9_DK_mean_mean_degree",
                "t1_vabsabcabc_standard", "t1_age_years", 
  "PLV_6_9_DK_mean_degree_1" , "PLV_6_9_DK_SWI_1",
                "age_difference")

# Scale only the predictors
Vineland_data_scaled <- Vineland_data %>%
  mutate(across(all_of(predictors), ~ as.numeric(scale(.))))

#AGE GROUPS
Vineland_data_young = filter(Vineland_data_scaled, AgeBin == '6-15')
Vineland_data_middle =filter(Vineland_data_scaled, AgeBin == '15-22')
Vineland_data_old = filter(Vineland_data_scaled, AgeBin == '22-31')
```


#SLIDING WINDOW BY INDEX - SWI
```{r}
# 1. First, order the participants by age
Vineland_ordered <- Vineland_data_scaled %>%
  arrange(age_for_filtering)

# 2. Define the sliding window parameters
window_size <- 30
step_size <- 5
total_n <- nrow(Vineland_ordered)

# Calculate the absolute last possible start index
last_start_possible <- total_n - window_size + 1

# Generate indices: 1, 6, 11... 
start_indices <- seq(1, last_start_possible, by = step_size)

# FEATURE: If the step sequence missed the final index (52), add it manually
if (tail(start_indices, 1) != last_start_possible) {
  start_indices <- c(start_indices, last_start_possible)
}

results_list <- list()

# 3. The Sliding Loop (by index)
# We stop when the window can no longer fit 30 participants
for (start_idx in start_indices) {
  
  end_idx <- start_idx + window_size - 1
  
  # Extract the specific 30 participants for this bin
  bin_data <- Vineland_ordered[start_idx:end_idx, ]
  
  # Check for factor level diversity (e.g., both sexes must be present)
  if (length(unique(bin_data$t1_sex)) > 1) {
    
    # Run the GLM (Linear Model)
    m_bin <- lm(Vineland_difference ~ PLV_6_9_DK_mean_SWI + t1_fsiq + 
                t1_vabsabcabc_standard + t1_age_years * age_difference + t1_sex, 
                data = bin_data)
    
    
    # Extract stats for the specific predictor
    stats <- tidy(m_bin) %>% 
      filter(term == "PLV_6_9_DK_mean_SWI")
    
    if (nrow(stats) > 0) {
      results_list[[paste0("idx_", start_idx)]] <- data.frame(
        n_in_bin = nrow(bin_data),
        min_age = min(bin_data$age_for_filtering, na.rm = TRUE),
        max_age = max(bin_data$age_for_filtering, na.rm = TRUE),
        avg_age = mean(bin_data$age_for_filtering, na.rm = TRUE),
        beta_estimate = stats$estimate,
        std_error = stats$std.error,
        p_value = stats$p.value
        
      )
    }
  }
}

# 4. Combine into final dataframe
rolling_results_idx <- bind_rows(results_list)

rolling_results_idx <- rolling_results_idx %>%
  mutate(p_FDR = p.adjust(p_value, method = "BH"))

rolling_results_idx <- rolling_results_idx %>%
  mutate(sig_star = ifelse(p_FDR < 0.05, "*", ""))

#from the rolling results df, remove the second to last row
rolling_results_idx <- rolling_results_idx[- (nrow(rolling_results_idx) - 1), ]

# View the output
print(rolling_results_idx)
```

```{r}
rolling_SWI = ggplot(rolling_results_idx, aes(x = avg_age, y = beta_estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  geom_line(color = "royalblue", size = 1) +
  geom_point() +
  geom_ribbon(aes(ymin = beta_estimate - std_error, 
                  ymax = beta_estimate + std_error), 
              alpha = 0.2, fill = "royalblue") +
  labs(title = "f) Effect size of SWI on ΔABC score across age",
       x = "Average Age in Bin",
       y = "Estimated coefficient - SWI") +
  geom_text(aes(label = sig_star, y = 0.5), 
            size = 8, 
            color = "black") +
  scale_x_continuous(breaks = seq(6, 32, by = 2)) +
  theme_minimal()+
    theme(aspect.ratio = 0.6,panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))


rolling_SWI
```

#SLIDING WINDOW BY INDEX - MD
```{r}
# 1. First, order the participants by age
Vineland_ordered <- Vineland_data_scaled %>%
  arrange(age_for_filtering)

# 2. Define the sliding window parameters
window_size <- 30
step_size <- 5
total_n <- nrow(Vineland_ordered)

# Calculate the absolute last possible start index
last_start_possible <- total_n - window_size + 1

# Generate indices: 1, 6, 11... 
start_indices <- seq(1, last_start_possible, by = step_size)

# FEATURE: If the step sequence missed the final index (52), add it manually
if (tail(start_indices, 1) != last_start_possible) {
  start_indices <- c(start_indices, last_start_possible)
}

results_list <- list()

# 3. The Sliding Loop (by index)
# We stop when the window can no longer fit 30 participants
for (start_idx in start_indices) {
  
  end_idx <- start_idx + window_size - 1
  
  # Extract the specific 30 participants for this bin
  bin_data <- Vineland_ordered[start_idx:end_idx, ]
  
  # Check for factor level diversity (e.g., both sexes must be present)
  if (length(unique(bin_data$t1_sex)) > 1 
      # && length(unique(bin_data$t1_site)) > 1
      ) {
    
    # Run the GLM (Linear Model)
    
        m_bin <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_fsiq + 
                t1_vabsabcabc_standard + t1_age_years * age_difference + t1_sex 
                #+ t1_site
                , 
                data = bin_data)
    
    # Extract stats for the specific predictor
    stats <- tidy(m_bin) %>% 
      filter(term == "PLV_6_9_DK_mean_mean_degree")
    
    if (nrow(stats) > 0) {
      results_list[[paste0("idx_", start_idx)]] <- data.frame(
        n_in_bin = nrow(bin_data),
        min_age = min(bin_data$age_for_filtering, na.rm = TRUE),
        max_age = max(bin_data$age_for_filtering, na.rm = TRUE),
        avg_age = mean(bin_data$age_for_filtering, na.rm = TRUE),
        beta_estimate = stats$estimate,
        std_error = stats$std.error,
        p_value = stats$p.value
        
      )
    }
  }
}

# 4. Combine into final dataframe
rolling_results_idx <- bind_rows(results_list)

rolling_results_idx <- rolling_results_idx %>%
  mutate(p_FDR = p.adjust(p_value, method = "BH"))

rolling_results_idx <- rolling_results_idx %>%
  mutate(sig_star = ifelse(p_FDR < 0.05, "*", ""))

#from the rolling results df, remove the second to last row
rolling_results_idx <- rolling_results_idx[- (nrow(rolling_results_idx) - 1), ]

# View the output
print(rolling_results_idx)
```


```{r}
rolling_MD = ggplot(rolling_results_idx, aes(x = avg_age, y = beta_estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  geom_line(color = "royalblue", size = 1) +
  geom_point() +
  geom_ribbon(aes(ymin = beta_estimate - std_error, 
                  ymax = beta_estimate + std_error), 
              alpha = 0.2, fill = "royalblue") +
  labs(title = "e) Effect size of mean degree on ΔABC score across age",
       x = "Average Age in Bin",
       y = "Estimated coefficient - mean degree") +
  geom_text(aes(label = sig_star, y = 10), 
            size = 8, 
            color = "black") +
  scale_x_continuous(breaks = seq(6, 32, by = 2)) +
  theme_minimal()+
    theme(aspect.ratio = 0.6,panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))

rolling_MD
```

#Figure 2 grid  
```{r}
combined_plot = grid.arrange(

  MD_all, SWI_all, MD_mid, 

  SWI_mid, rolling_MD, rolling_SWI, 

  ncol = 2, nrow = 3

)

combined_plot
#setwd()
ggsave("combined_graphs.png", plot = combined_plot, width = 13, height = 13, dpi = 600)
```

# connectome protocol PLOTS
```{r}
vineland_ASD_middle <- Vineland_data_middle

m1 <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + t1_vabsabcabc_standard + t1_fsiq +  t1_age_years*age_difference +t1_sex + t1_site, data = vineland_ASD_middle)

#ASD NON ID MIDDLE MD
MD_15_21 = ggplot(vineland_ASD_middle, aes(y=predict(m1), x= Vineland_difference)) +
  geom_point() +geom_smooth(method='lm', se = FALSE) +
  geom_abline(intercept=0, slope=1) +  stat_cor(
    method          = "pearson",
    cor.coef.name   = "r",       # lower‐case “r”
    r.digits        = 2,         # two decimal places for r
    p.accuracy      = 0.001,     # p < 0.001 for very small p
    output.type     = "text",    # plain text, not plotmath
    label.sep       = ", "       # “r = 0.63, p < 0.001”
  )+
  labs(x='Actual Values', y='Predicted Values', title='a) Actual vs predicted values of ∆ABC from the model\n containing MD for 15-24-year-old autistic people, n = 38')+ xlim(-40, 30) + ylim(-40, 30)+
 theme_bw()+ theme(aspect.ratio=1,  plot.title = element_text(size = 10))


m2 <- lm(Vineland_difference ~  PLV_6_9_DK_mean_SWI + t1_vabsabcabc_standard + t1_fsiq + t1_age_years*age_difference + t1_sex, data = vineland_ASD_middle)

SWI_15_21 = ggplot(vineland_ASD_middle, aes(x=Vineland_difference, y=  predict(m2))) +
  geom_point() +geom_smooth(method='lm', se = FALSE) +
  geom_abline(intercept=0, slope=1) +  stat_cor(
    method          = "pearson",
    cor.coef.name   = "r",       # lower‐case “r”
    r.digits        = 2,         # two decimal places for r
    p.accuracy      = 0.001,     # p < 0.001 for very small p
    output.type     = "text",    # plain text, not plotmath
    label.sep       = ", "       # “r = 0.63, p < 0.001”
  )+
  labs(x='Actual Values', y='Predicted Values', title='c) Actual vs predicted values of ∆ABC from the model\n containing SWI for 15-24-year-old autistic people, n = 38')+
 theme_bw()+ theme(aspect.ratio=1, plot.title = element_text(size = 10))  + xlim(-40, 30) + ylim(-40, 30)



vineland_ASD <- Vineland_data

m3 <- lm(Vineland_difference ~ (PLV_6_9_DK_mean_SWI) + t1_vabsabcabc_standard +t1_fsiq + t1_age_years*age_difference + t1_site, data = vineland_ASD)

SWI_6_31 = ggplot(vineland_ASD, aes(y=predict(m3), x= Vineland_difference)) +
  geom_point() +geom_smooth(method='lm', se = FALSE) +
  geom_abline(intercept=0, slope=1) + 
  stat_cor(
    method          = "pearson",
    cor.coef.name   = "r",       # lower‐case “r”
    r.digits        = 2,         # two decimal places for r
    p.accuracy      = 0.001,     # p < 0.001 for very small p
    output.type     = "text",    # plain text, not plotmath
    label.sep       = ", "       # “r = 0.63, p < 0.001”
  )+
  labs(x='Actual Values', y='Predicted Values', title='b) Actual vs predicted values of ∆ABC from the model\n containing SWI for 6-31-year-old autistic people, n = 81') + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(size = 10)) + xlim(-40, 30) + ylim(-40, 30)                      
    

connectome_grid = ggpubr::ggarrange(MD_15_21, SWI_6_31, SWI_15_21,
            ncol = 2, nrow = 2)

#setwd()

ggsave(filename = "connectome_grid_figure.png", 
       plot = connectome_grid, 
       width = 12,      # Width in inches
       height = 12,      # Height in inches
       dpi = 300,       # 300 DPI is standard for publication-quality images
       bg = "white")    # Ensures the background is white, not transparent

connectome

```

#p values doubleres with IQ - 12/6/2026 - SWI ALL AGES
```{r}
# 1. Isolate the data and drop NAs 
# CRITICAL: If we don't drop NAs first, model.matrix will silently drop them, 
# but our 'y' vector won't, causing a length mismatch error later!
clean_data <- Vineland_data %>%
  select(Vineland_difference, PLV_6_9_DK_mean_SWI, t1_fsiq, 
         t1_vabsabcabc_standard, t1_age_years, age_difference, t1_site) %>%
  drop_na()

# 2. Define the outcome variable (y)
y <- clean_data$Vineland_difference

# 3. Create the numeric predictor matrix
# The '- 1' at the end tells R not to create an intercept column, 
# as double residualization typically handles centering natively.
X_matrix <- model.matrix(
  ~ PLV_6_9_DK_mean_SWI + t1_fsiq + t1_vabsabcabc_standard + 
    t1_age_years * age_difference + t1_site - 1, 
  data = clean_data
)

# Convert back to a standard dataframe for the doubleres function
X_df <- as.data.frame(X_matrix)

# 4. Run the Double Residualization
set.seed(150)
swi_model_result <- doubleres(y, X_df, nperm = 9999, nfolds = 5)

# View results
swi_model_result

```

#p values doubleres with IQ - 12/6/2026 - MD ALL AGES
```{r}

# 1. Isolate the necessary columns and drop NAs
# Note: I used 't1_age' instead of 't1_age_years' based on your formula
clean_data <- Vineland_data %>%
  select(Vineland_difference, PLV_6_9_DK_mean_mean_degree, t1_vabsabcabc_standard, 
         t1_fsiq, t1_age, age_difference, t1_site) %>%
  drop_na()

# 2. Define the outcome variable (y)
y <- clean_data$Vineland_difference

# 3. Create the numeric predictor matrix
# model.matrix automatically calculates the interaction and dummy codes the sites.
# The '- 1' removes the intercept column.
X_matrix <- model.matrix(
  ~ PLV_6_9_DK_mean_mean_degree + t1_vabsabcabc_standard + t1_fsiq + 
    t1_age * age_difference + t1_site - 1, 
  data = clean_data
)

# Convert the matrix back into a standard dataframe format for doubleres
X_df <- as.data.frame(X_matrix)

# 4. Run the Double Residualization
set.seed(150)
mean_degree_result <- doubleres(y, X_df, nperm = 9999, nfolds = 5)

# View results
mean_degree_result
```

#p values doubleres with IQ - 12/6/2026 - SWI YOUTH
```{r}

# 1. Isolate the data and drop NAs 
clean_data <- Vineland_data_middle %>%
  select(Vineland_difference, PLV_6_9_DK_mean_SWI, t1_fsiq, 
         t1_vabsabcabc_standard, t1_age_years, age_difference, t1_sex) %>%
  drop_na()

# 2. Define the outcome variable (y)
y <- clean_data$Vineland_difference

# 3. Create the numeric predictor matrix
# model.matrix handles the interaction and dummy codes t1_sex
# The '- 1' removes the intercept
X_matrix <- model.matrix(
  ~ PLV_6_9_DK_mean_SWI + t1_fsiq + t1_vabsabcabc_standard + 
    t1_age_years * age_difference + t1_sex - 1, 
  data = clean_data
)

# Convert to standard dataframe
X_df <- as.data.frame(X_matrix)

# 4. Run the Double Residualization
set.seed(150)
swi_middle_result <- doubleres(y, X_df, nperm = 9999, nfolds = 5)

# 5. Extract the results
# Print the full result to the console to see the summary
print(swi_middle_result)
```

#p values doubleres IQ, MD middle
```{r}
# 1. Isolate the data and drop NAs 
clean_data <- Vineland_data_middle %>%
  select(Vineland_difference, PLV_6_9_DK_mean_mean_degree, t1_fsiq, 
         t1_vabsabcabc_standard, t1_age, age_difference, t1_sex, t1_site) %>%
  drop_na()

# 2. Define the outcome variable (y)
y <- clean_data$Vineland_difference

# 3. Create the numeric predictor matrix
# model.matrix handles the interaction and dummy codes both t1_sex and t1_site
# The '- 1' removes the intercept
X_matrix <- model.matrix(
  ~ PLV_6_9_DK_mean_mean_degree + t1_fsiq + t1_vabsabcabc_standard + 
    t1_age * age_difference + t1_sex + t1_site - 1, 
  data = clean_data
)

# Convert to standard dataframe format for doubleres
X_df <- as.data.frame(X_matrix)

# 4. Run the Double Residualization
set.seed(150)
mean_degree_middle_result <- doubleres(y, X_df, nperm = 9999, nfolds = 5)

# 5. View the results
print(mean_degree_middle_result)
```

#10 fold cross validation for paper
```{r}
train.control<- trainControl(method="cv", number = 10)

#6-31 SWI
model <- train(Vineland_difference ~ PLV_6_9_DK_mean_SWI + t1_vabsabcabc_standard +  t1_fsiq  + t1_age_years*age_difference + t1_site, data = Vineland_data, method = "lm", trControl = train.control)
print(model)

#SWI 15-24
model <- train(Vineland_difference ~ t1_sex + t1_fsiq + PLV_6_9_DK_mean_SWI + t1_vabsabcabc_standard + t1_age_years*age_difference, data = Vineland_data_middle, method = "lm", trControl = train.control)
print(model)

#MD 15-24
model <- train(Vineland_difference ~ t1_vabsabcabc_standard +  t1_fsiq + PLV_6_9_DK_mean_mean_degree + t1_age_years*age_difference + t1_site + t1_sex, data = Vineland_data_middle, method = "lm", trControl = train.control)
print(model)

```

#levene's test for variance
```{r}
variance_data_set = filter(Vineland_data, AgeBin != '22-31')
levene_test(variance_data_set, Vineland_difference ~ AgeBin)
levene_test(variance_data_set, PLV_6_9_DK_mean_SWI ~ AgeBin)
levene_test(variance_data_set, PLV_6_9_DK_mean_mean_degree ~ AgeBin)
```


#LEAVE ONE OUT CROSS VALIDATION - MEAN DEGREE, VINELAND MIDDLE - WITH PERMUTATION TEST
```{r}

categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else if (x <= -6) {
    return("decrease")
  } else {
    return("no_change")
  }
}

# Initialize
n <- nrow(Vineland_data_middle)
actual_category <- character(n)
predicted_category <- character(n)

# Loop through each participant for LOOCV
for (i in 1:n) {
  # Training data (leave one out)
  train_data <- Vineland_data_middle[-i, ]
  test_data <- Vineland_data_middle[i, ]
  
  # Fit model
  model_loocv <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + 
                    t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                    t1_sex + t1_site, data = train_data)
  
  # Predict on left-out sample
  predicted_value <- predict(model_loocv, newdata = test_data)
  
  # Store categorized actual and predicted values
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
  predicted_category[i] <- categorize_change(predicted_value)
}

# Accuracy
correct <- actual_category == predicted_category
overall_accuracy <- mean(correct)
cat("LOOCV category prediction accuracy:", round(overall_accuracy * 100, 2), "%\n")

# Confusion matrix
print(table(Actual = actual_category, Predicted = predicted_category))

# Permutation test
n_permutations <- 1000
permuted_accuracies <- numeric(n_permutations) #vector of 1000 0s

for (p in 1:n_permutations) {
  permuted_actual <- sample(actual_category)  # Shuffle labels
  permuted_correct <- permuted_actual == predicted_category
  permuted_accuracies[p] <- mean(permuted_correct)
}

# Step 6: Compute p-value (one-sided: observed > permuted)
p_value <- mean(permuted_accuracies >= overall_accuracy) #you can't have a negative percentage
cat("Permutation test p-value:", p_value, "\n")

# Optional: histogram of null distribution
hist(permuted_accuracies, breaks = 30, main = "Permutation Null Distribution",
     xlab = "Accuracy", xlim = c(0, 1))
abline(v = overall_accuracy, col = "red", lwd = 2)

```

#LEAVE ONE OUT CROSS VALIDATION - SWI, VINELAND MIDDLE
```{r}

categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else if (x <= -6) {
    return("decrease")
  } else {
    return("no_change")
  }
}

# Initialize
n <- nrow(Vineland_data_middle)
actual_category <- character(n)
predicted_category <- character(n)

# Loop through each participant for LOOCV
for (i in 1:n) {
  # Training data (leave one out)
  train_data <- Vineland_data_middle[-i, ]
  test_data <- Vineland_data_middle[i, ]
  
  # Fit model
  model_loocv <- lm(Vineland_difference ~ PLV_6_9_DK_mean_SWI + 
                    t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                    t1_sex, data = train_data)
  
  # Predict on left-out sample
  predicted_value <- predict(model_loocv, newdata = test_data)
  
  # Store categorized actual and predicted values
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
  predicted_category[i] <- categorize_change(predicted_value)
}

# Accuracy
correct <- actual_category == predicted_category
overall_accuracy <- mean(correct)
cat("LOOCV category prediction accuracy:", round(overall_accuracy * 100, 2), "%\n")

# Confusion matrix
print(table(Actual = actual_category, Predicted = predicted_category))

# Permutation test
n_permutations <- 1000
permuted_accuracies <- numeric(n_permutations) #vector of 1000 0s

for (p in 1:n_permutations) {
  permuted_actual <- sample(actual_category)  # Shuffle labels
  permuted_correct <- permuted_actual == predicted_category
  permuted_accuracies[p] <- mean(permuted_correct)
}

# Step 6: Compute p-value (one-sided: observed > permuted)
p_value <- mean(permuted_accuracies >= overall_accuracy) #you can't have a negative percentage
cat("Permutation test p-value:", p_value, "\n")


```


#AUC INCREASES VS NON INCREASES IN THE FUNCTION - MIDDLE MEAN DEGREE
```{r}
n <- nrow(Vineland_data_middle)
actual_category <- character(n)
predicted_category <- character(n)
predicted_value_all <- numeric(n)  # Store raw predicted values for ROC

# Step 1: Categorization function
categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else {
    return("no_increase")
  }
}

# Step 2: LOOCV
for (i in 1:n) {
  train_data <- Vineland_data_middle[-i, ]
  test_data <- Vineland_data_middle[i, ]
  
  model_loocv <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + 
                    t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                    t1_sex + t1_site, data = train_data)
  
  predicted_value <- predict(model_loocv, newdata = test_data)
  
  predicted_value_all[i] <- predicted_value
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
  predicted_category[i] <- categorize_change(predicted_value)
}

# Step 3: Subset to increase vs decrease
valid_idx <- which(actual_category %in% c("increase", "no_increase")) 
actual_bin <- ifelse(actual_category[valid_idx] == "increase", 1, 0) #Converts the actual category labels into binary numeric form:"increase" → 1, "decrease" → 0
predicted_bin <- ifelse(predicted_category[valid_idx] == "increase", 1, 0)  
predicted_scores <- predicted_value_all[valid_idx]

# Step 4: AUC using raw predicted values
roc_obj <- roc(actual_bin, predicted_scores)
auc_value <- pROC::auc(roc_obj)

# Step 5: Sensitivity and Specificity
conf_mat <- table(Predicted = predicted_bin, Actual = actual_bin)

TP <- conf_mat["1", "1"]
TN <- conf_mat["0", "0"]
FP <- conf_mat["1", "0"]
FN <- conf_mat["0", "1"]

sensitivity <- TP / (TP + FN)
specificity <- TN / (TN + FP)

# Step 6: Output results
cat("AUC:", round(auc_value, 3), "\n")
cat("Sensitivity (recall for 'increase'):", round(sensitivity, 3), "\n")
cat("Specificity (recall for 'no_increase'):", round(specificity, 3), "\n")

# Compute 95% CI for AUC (using bootstrapping by default)
auc_ci <- ci.auc(roc_obj)
print(auc_ci)

plot(roc_obj,
     col = "#1c61b6",        # Curve color
     lwd = 2,                # Line width
     main = "ROC Curve: Increasing vs not-increasing adaptive function (n = 38)",
     print.auc = TRUE,       # Display AUC on the plot
     print.auc.cex = 1.2,    # Font size of AUC
     legacy.axes = TRUE,     # Optional: TPR on Y-axis, FPR on X-axis
     xlab = "False Positive Rate (1 - Specificity)",
     ylab = "True Positive Rate (Sensitivity)")



```

#AUC SWI MIDDLE 
```{r}
Vineland_middle = Vineland_data_middle

n <- nrow(Vineland_middle)
actual_category <- character(n)
predicted_category <- character(n)
predicted_value_all <- numeric(n)  # Store raw predicted values for ROC

# Step 1: Categorization function
categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else {
    return("no_increase")
  }
}

# Step 2: LOOCV
for (i in 1:n) {
  train_data <- Vineland_middle[-i, ]
  test_data <- Vineland_middle[i, ]
  
  model_loocv <- lm(Vineland_difference ~ scale(PLV_6_9_DK_mean_SWI) + 
                    t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                    t1_sex, data = train_data)
  
  predicted_value <- predict(model_loocv, newdata = test_data)
  
  predicted_value_all[i] <- predicted_value
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
  predicted_category[i] <- categorize_change(predicted_value)
}

# Step 3: Subset to increase vs decrease
actual_bin <- ifelse(actual_category == "increase", 1, 0)
predicted_bin <- ifelse(predicted_category == "increase", 1, 0)
predicted_scores <- predicted_value_all  # continuous scores

# Step 4: AUC using raw predicted values
roc_obj <- roc(actual_bin, predicted_scores)
auc_value <- pROC::auc(roc_obj)

# Step 5: Sensitivity and Specificity
conf_mat <- table(Predicted = predicted_bin, Actual = actual_bin)

TP <- conf_mat["1", "1"]
TN <- conf_mat["0", "0"]
FP <- conf_mat["1", "0"]
FN <- conf_mat["0", "1"]

sensitivity <- TP / (TP + FN)
specificity <- TN / (TN + FP)

# Step 6: Output results
cat("AUC:", round(auc_value, 3), "\n")
cat("Sensitivity (recall for 'increase'):", round(sensitivity, 3), "\n")
cat("Specificity (recall for 'no_increase'):", round(specificity, 3), "\n")

plot(roc_obj,
     col = "#1c61b6",        # Curve color
     lwd = 2,                # Line width
     main = "ROC Curve: Increased Vineland Score",
     print.auc = TRUE,       # Display AUC on the plot
     print.auc.cex = 1.2,    # Font size of AUC
     legacy.axes = TRUE,     # Optional: TPR on Y-axis, FPR on X-axis
     xlab = "False Positive Rate (1 - Specificity)",
     ylab = "True Positive Rate (Sensitivity)")

# Optional: add diagonal reference line
abline(a = 0, b = 1, lty = 2, col = "gray")

# Compute 95% CI for AUC (using bootstrapping by default)
auc_ci <- ci.auc(roc_obj)
print(auc_ci)


```

#COMBINED ROC MD SWI MIDDLE
```{r}
Vineland_middle <- Vineland_data_middle
n <- nrow(Vineland_middle)

# Initialize storage for both models
actual_category <- character(n)
pred_swi_all <- numeric(n)
pred_degree_all <- numeric(n)

# Step 1: Categorization function
categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else {
    return("no_increase")
  }
}

# Step 2: Single LOOCV Loop for BOTH models
for (i in 1:n) {
  train_data <- Vineland_middle[-i, ]
  test_data <- Vineland_middle[i, ]
  
  # Model 1: SWI
  model_swi <- lm(Vineland_difference ~ scale(PLV_6_9_DK_mean_SWI) + 
                    t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                    t1_sex, data = train_data)
  
  # Model 2: Mean Degree
  model_degree <- lm(Vineland_difference ~ PLV_6_9_DK_mean_mean_degree + 
                       t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                       t1_sex + t1_site, data = train_data)
  
  # Store predictions
  pred_swi_all[i] <- predict(model_swi, newdata = test_data)
  pred_degree_all[i] <- predict(model_degree, newdata = test_data)
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
}

# Step 3: Define binary outcomes
actual_bin <- ifelse(actual_category == "increase", 1, 0)

# Step 4: Generate ROC objects
roc_swi <- roc(actual_bin, pred_swi_all, quiet = TRUE)
roc_degree <- roc(actual_bin, pred_degree_all, quiet = TRUE)

# Step 5: Extract Coordinates for Threshold = 6
# This finds the exact Sensitivity and Specificity when the prediction cutoff is exactly 6
coords_swi <- coords(roc_swi, x = 6, input = "threshold", ret = c("specificity", "sensitivity"))
coords_degree <- coords(roc_degree, x = 6, input = "threshold", ret = c("specificity", "sensitivity"))

# Step 6: Plotting
# Force a 1:1 square aspect ratio for the plot region
roc_plot_middle <- function() {
par(pty = "s") 

# Plot the primary model (Mean Degree)
plot(roc_degree,
     col = "#d95f02",        
     lwd = 2,                # Line width
     lty = 1, 
     main = "Increased vs not-increased adaptive \n function in 15-24-year-olds (n = 38)",
     legacy.axes = TRUE,     # TPR on Y-axis, FPR on X-axis (labels 0 to 1)
     xlab = "False Positive Rate (1 - Specificity)",
     ylab = "True Positive Rate (Sensitivity)",
     cex.lab = 1.4,          # Scales axis label font size up (approx 14pt)
     identity = TRUE,        # Let pROC draw the chance line automatically (fixes the flip)
     identity.lty = 3,       
     identity.col = "gray50",
     identity.lwd = 1.5)

# Add the second model (SWI) to the same plot
plot(roc_swi, 
     col = "#1c61b6"    ,    
     lwd = 2, 
     add = TRUE)             # Add to existing plot

# Add points marking the threshold = 6
# Because pROC's internal X-axis is Specificity (even with legacy.axes=TRUE), 
# we use the raw specificity value for the X coordinate so it plots in the right place.
points(x = coords_degree$specificity, y = coords_degree$sensitivity, 
       pch = 19, col = "#d95f02", cex = 1.5)
points(x = coords_swi$specificity, y = coords_swi$sensitivity, 
       pch = 19, col = "#1c61b6", cex = 1.5)

# Create legend labels with explicit pROC namespace and numeric coercion
auc_degree_label <- paste0("MD Model (AUC = ", round(as.numeric(pROC::auc(roc_degree)), 2), ")")
auc_swi_label <- paste0("SWI Model (AUC = ", round(as.numeric(pROC::auc(roc_swi)), 2), ")")

# Add the legend to the bottom right
legend("bottomright", 
       legend = c(auc_degree_label, auc_swi_label, "Threshold Cut-off = 6"),
       col = c("#d95f02", "#1c61b6","black", "gray50"),
       lwd = c(2, 2, NA, 1.5),
       lty = c(1, 1, NA, 3),
       pch = c(NA, NA, 19, NA), 
       bty = "n",               # Removes the box around the legend
       cex = 1)               # Slightly scales down text to fit nicely

}

roc_plot_middle()

```


#AUC VINELAND ALL - increase vs not
```{r}
n <- nrow(Vineland_data)
actual_category <- character(n)
predicted_category <- character(n)
predicted_value_all <- numeric(n)  # Store raw predicted values for ROC

# Step 1: Categorization function
categorize_change <- function(x) {
  if (x >= 6) {
    return("increase")
  } else {
    return("no_increase")
  }
}

# Step 2: LOOCV
for (i in 1:n) {
  train_data <- Vineland_data[-i, ]
  test_data <- Vineland_data[i, ]
  
  model_loocv <- lm(Vineland_difference ~ scale(PLV_6_9_DK_mean_SWI) + 
                      t1_fsiq + t1_vabsabcabc_standard + t1_age*age_difference + 
                      t1_site, data = train_data)
  
  predicted_value <- predict(model_loocv, newdata = test_data)
  
  predicted_value_all[i] <- predicted_value
  actual_category[i] <- categorize_change(test_data$Vineland_difference)
  predicted_category[i] <- categorize_change(predicted_value)
}

# Step 3: Subset to increase vs decrease
actual_bin <- ifelse(actual_category == "increase", 1, 0)
predicted_bin <- ifelse(predicted_category == "increase", 1, 0)
predicted_scores <- predicted_value_all  # continuous scores

# Step 4: ROC and AUC calculation
roc_obj <- roc(actual_bin, predicted_scores, quiet = TRUE)
auc_value <- pROC::auc(roc_obj)

# Extract coordinates for the specific threshold of 6
coords_swi_all <- coords(roc_obj, x = 6, input = "threshold", ret = c("specificity", "sensitivity"))

# Step 5: Sensitivity and Specificity Check
conf_mat <- table(Predicted = predicted_bin, Actual = actual_bin)

TP <- conf_mat["1", "1"]
TN <- conf_mat["0", "0"]
FP <- conf_mat["1", "0"]
FN <- conf_mat["0", "1"]

sensitivity <- TP / (TP + FN)
specificity <- TN / (TN + FP)

cat("AUC:", round(auc_value, 3), "\n")
cat("Sensitivity (recall for 'increase'):", round(sensitivity, 3), "\n")
cat("Specificity (recall for 'no_increase'):", round(specificity, 3), "\n")


# ==========================================
# Step 6: Plotting Function
# ==========================================
draw_roc_plot_81 <- function() {
  # Force a 1:1 square aspect ratio
  par(pty = "s") 
  
  # Plot the ROC curve
  plot(roc_obj,
       col = "#1c61b6",        # Blue curve color
       lwd = 2,                # Line width
       main = "Increased vs not-increased adaptive \n function in 6-31-year-olds (n = 81)",
       legacy.axes = TRUE,     # TPR on Y-axis, FPR on X-axis (0 to 1)
       xlab = "False Positive Rate (1 - Specificity)",
       ylab = "True Positive Rate (Sensitivity)",
       cex.lab = 1.4,          # Scales axis label font size up (approx 14pt)
       identity = TRUE,        # Let pROC draw the chance line automatically
       identity.lty = 3,       
       identity.col = "gray50",
       identity.lwd = 1.5)
  
  # Add point marking the threshold = 6
  points(x = coords_swi_all$specificity, y = coords_swi_all$sensitivity, 
         pch = 19, col = "#1c61b6", cex = 1.5)
  
  # Create legend label safely
  auc_label <- paste0("SWI Model (AUC = ", round(as.numeric(pROC::auc(roc_obj)), 2), ")")
  
  # Add the legend to the bottom right
  legend("bottomright", 
         legend = c(auc_label, "Threshold Cut-off = 6"),
         col = c("#1c61b6", "black", "gray50"),
         lwd = c(2, NA, 1.5),
         lty = c(1, NA, 3),
         pch = c(NA, 19, NA), 
         bty = "n",               
         cex = 1)               
}

# Call the function to display the plot
draw_roc_plot_81()
```

```{r}
final_grid <- plot_grid(~roc_plot_middle(), ~draw_roc_plot_81(), labels = c("b)", "c)"))

print(final_grid)

#setwd()

ggsave(filename = "ROC_grid_figure.png", 
       plot = final_grid, 
       width = 12,      # Width in inches
       height = 6,      # Height in inches
       dpi = 300,       # 300 DPI is standard for publication-quality images
       bg = "white")    # Ensures the background is white, not transparent
```


#GRAPHS FOR PAPER - 21/3/24 - AGE VS GRAPH THEORY - group differences
```{r}

PLV_6_9_DK_mean_mean_degree_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + I(t1_age_years^2) + t1_site + t1_sex, data = young))

#YOUNG MD
number_matricies <- ggplot(young, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_mean_degree_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
    stat_compare_means(method = "t.test")+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#MD middle
PLV_6_9_DK_mean_md_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + t1_sex + t1_site, data = middle))

number_matricies <- ggplot(middle, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_md_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
  stat_compare_means(method = "t.test")+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#MD OLD
PLV_6_9_DK_mean_mean_degree_resid <- resid(lm(PLV_6_9_DK_mean_mean_degree ~ t1_age_years + I(t1_age_years^2) + t1_site, data = old))

number_matricies <- ggplot(old, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_mean_degree_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
  stat_compare_means(method = "t.test")+
  labs(x="", y = "Mean degree (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#YOUNG SWI
PLV_6_9_DK_mean_SWI_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_age_years + I(t1_age_years^2) + t1_site, data = young))

number_matricies <- ggplot(young, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
  stat_compare_means(method = "t.test")+
  labs(x="", y = "Small world index (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

# MIDDLE SWI
PLV_6_9_DK_mean_SWI_resid <- resid(lm(PLV_6_9_DK_mean_SWI ~ t1_age_years + t1_site  + t1_sex , data = middle))

number_matricies <- ggplot(middle, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI_resid, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
  stat_compare_means(method = "t.test")+
  labs(x="", y = "Small world index (residual)", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies

#SWI OLD
number_matricies <- ggplot(old, aes(x = ASD_TDC, y = PLV_6_9_DK_mean_SWI, color = ASD_TDC))+
  geom_jitter()+ geom_boxplot(alpha = 0.5)+
  scale_color_manual(values=c("#0086EA","orange"))+
  stat_compare_means(method = "t.test")+
  labs(x="", y = "Small world index", col = "Group", shape = "Group") +
  theme(panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))
number_matricies


```

#co-occurring conditions by age
```{r}
b_nonID <- b_nonID %>%
  mutate(
    ADHD = case_when(
      (Proband_ADHD_Inattention %in% 2 | Proband_ADHD_Hyperactive %in% 2 | Proband_ADHD_Impulsive %in% 2) | 
         (`t1_Do you have any of the following:(Attention deficit hyperactivity disorder (ADHD))` %in% "Y" & (!(Proband_ADHD_Inattention %in% c(0, 1)) & !(Proband_ADHD_Hyperactive %in% c(0, 1)) & !(Proband_ADHD_Impulsive %in% c(0, 1))))
      ~ "Y",
      
       (Proband_ADHD_Inattention %in% c(0, 1) & Proband_ADHD_Hyperactive %in% c(0, 1) & Proband_ADHD_Impulsive %in% c(0, 1)) |
         (`t1_Do you have any of the following:(Attention deficit hyperactivity disorder (ADHD))` %in% c("N", "NK") &  !(Proband_ADHD_Inattention %in% 2 | Proband_ADHD_Hyperactive %in% 2 | Proband_ADHD_Impulsive %in% 2))
      
         ~ "N",
      
      # -------------------------------------------------------------------
      # RULE 3: Else = Missing
      # -------------------------------------------------------------------
      # If a row doesn't meet the "Y" or "N" conditions above, make it NA
      TRUE ~ NA_character_
    ),
      
    
    
    Dyspraxia = ifelse(Proband_Dyspraxia == 2, "Y", "N"),
    
    DyslexiaDyscalculia = ifelse(Proband_SLP_DyslexiaDyscalculia == 2, "Y", "N"),
    
    GDD = ifelse(Proband_ID_GDD == 2, "Y", "N"),
    
    OCD = case_when(
      # -------------------------------------------------------------------
      # RULE 1: OCD = Y
      # -------------------------------------------------------------------
      Proband_OCD %in% 2 | 
        (`t1_Do you have any of the following:(Obsessive compulsive disorder)` %in% "Y" & !(Proband_OCD %in% c(0, 1))) 
      ~ "Y",
      
      # -------------------------------------------------------------------
      # RULE 2: OCD = N
      # -------------------------------------------------------------------
      Proband_OCD %in% c(0, 1) | 
        (`t1_Do you have any of the following:(Obsessive compulsive disorder)` %in% c("N", "NK") & !(Proband_OCD %in% 2)) 
      ~ "N",
      
      # -------------------------------------------------------------------
      # RULE 3: Else = Missing
      # -------------------------------------------------------------------
      # If a row doesn't meet the "Y" or "N" conditions above, make it NA
      TRUE ~ NA_character_
    ),
    
    # OCD = ifelse(
    #   Proband_OCD == 2 |
    #     `t1_Do you have any of the following:(Obsessive compulsive disorder)` == "Y" & is.na(Proband_OCD), 
    #   "Y", "N"),
    
    Anxiety = case_when(
  # -------------------------------------------------------------------
  # RULE 1: Anxiety = Y
  # -------------------------------------------------------------------
  Proband_Anxiety %in% 2 | 
  (`t1_Do you have any of the following:(Anxiety disorder)` %in% "Y" & !(Proband_Anxiety %in% c(0, 1))) 
  ~ "Y",
  
  # -------------------------------------------------------------------
  # RULE 2: Anxiety = N
  # -------------------------------------------------------------------
  Proband_Anxiety %in% c(0, 1) | 
  (`t1_Do you have any of the following:(Anxiety disorder)` %in% c("N", "NK") & !(Proband_Anxiety %in% 2)) 
  ~ "N",
  
  # -------------------------------------------------------------------
  # RULE 3: Else = Missing
  # -------------------------------------------------------------------
  # If a row doesn't meet the "Y" or "N" conditions above, make it NA
  TRUE ~ NA_character_
),

    
Depression = case_when(
  # -------------------------------------------------------------------
  # RULE 1: Depression = Y
  # -------------------------------------------------------------------
  Proband_Depression %in% 2 | 
  (`t1_Do you have any of the following:(Depression)` %in% "Y" & !(Proband_Depression %in% c(0, 1))) 
  ~ "Y",
  
  # -------------------------------------------------------------------
  # RULE 2: Depression = N
  # -------------------------------------------------------------------
  Proband_Depression %in% c(0, 1) | 
  (`t1_Do you have any of the following:(Depression)` %in% c("N", "NK") & !(Proband_Depression %in% 2)) 
  ~ "N",
  
  # -------------------------------------------------------------------
  # RULE 3: Else = Missing
  # -------------------------------------------------------------------
  # If a row doesn't meet the "Y" or "N" conditions above, make it NA
  TRUE ~ NA_character_
)

  )


# 1. Define the base dataset
summary_table <- b_nonID %>%
  select(AgeBin, ASD_TDC, t1_sex, t1_fsiq, ADHD, Dyspraxia, 
         DyslexiaDyscalculia, GDD, OCD, Anxiety, Depression, 
         t1_srs_tscore_parent)

summary_table$Dyspraxia = factor(summary_table$Dyspraxia, levels = c("N", "Y"))
summary_table$GDD = factor(summary_table$GDD, levels = c("N", "Y"))

my_controls <- tableby.control(
  cat.stats = "countN", # Changes output to "Count / Total" format (e.g., 2/3)
  cat.simplify = TRUE    # Drops the redundant first level for binary variables
)

# 3. Create the tables using the control argument
tab_6_15 <- tableby(ASD_TDC ~ . - AgeBin, 
                    data = filter(summary_table, AgeBin == "6-15"),control = my_controls)
df_6_15 <- as.data.frame(summary(tab_6_15, text = TRUE))

tab_15_22 <- tableby(ASD_TDC ~ . - AgeBin, 
                     data = filter(summary_table, AgeBin == "15-22"),control = my_controls)
df_15_22 <- as.data.frame(summary(tab_15_22, text = TRUE))

tab_22_31 <- tableby(ASD_TDC ~ . - AgeBin, 
                     data = filter(summary_table, AgeBin == "22-31"),control = my_controls)

df_22_31 <- as.data.frame(summary(tab_22_31, text = TRUE))

# 4. Standardize the first column name so we can join on it
colnames(df_6_15)[1] <- "Variable"
colnames(df_15_22)[1] <- "Variable"
colnames(df_22_31)[1] <- "Variable"

# 5. get rid of N miss
df_6_15 <- df_6_15 %>%  filter(!str_detect(Variable, "^-\\s*N-Miss"))

df_15_22 <- df_15_22 %>% filter(!str_detect(Variable, "^-\\s*N-Miss"))

df_22_31 <- df_22_31 %>% filter(!str_detect(Variable, "^-\\s*N-Miss"))

#bind them
all_ages = cbind(df_6_15, df_15_22, df_22_31)

# 7. Export
#setwd("")
write.csv(all_ages, "Demographics_Summary_Robust_short.csv", row.names = FALSE)


```

#mean follow up interval
```{r}

summary_table <- Vineland_data %>%
  select(AgeBin, age_difference)
table_one <- tableby(AgeBin ~ ., data = summary_table)
summary(table_one, text = TRUE)

t.test(age_difference ~ AgeBin, data = summary_table)

ggplot(summary_table, aes(x = AgeBin, y = age_difference)) + geom_jitter() + stat_compare_means() + geom_boxplot() +theme_bw()
```

```{r}

ASD_nonID$AgeBin <- factor(ASD_nonID$AgeBin, levels = c("6-15", "15-22", "22-31"))

# Tell tableby exactly which statistics you want for numeric variables
my_controls <- tableby.control(
  numeric.stats = c("N", "mean", "sd", "range")
)
# 3. Create the table using the formula: GroupingVariable ~ Var1 + Var2 + Var3
tab <- tableby(AgeBin ~ Vineland_difference + 
                        t1_vabsabcabc_standard + 
                        t2_vabsabcabc_standard, 
               data = ASD_nonID, 
               control = my_controls)

# 4. Print the summary of the table
# (Using text = TRUE makes it print nicely right in your R console)
summary(tab)
```

#SRS Tscore self vs parent
```{r}
MS <- ggplot(ASD_nonID, aes(x = t1_srs_tscore_parent, y = t1_srs_tscore_self)) + geom_point()+
  geom_smooth(method='lm', se = FALSE)+
  stat_cor(method = "pearson") + theme_bw()
MS
```

#SRS rolling with age average
Prepare data
```{r}
b_nonID <- filter(b, ID_nonID == 'nonID')
ASD_nonID <- filter(b_nonID, t1_group == 'ASD')
ASD_SRS <- filter(ASD_nonID, t1_srs_tscore_parent != 'NA')

# Define the list of predictors from your formula
ASD_SRS$age_for_filtering <- ASD_SRS$t1_age_years

predictors <- c(
  "PLV_6_9_DK_mean_SWI", "t1_fsiq",
                "PLV_6_9_DK_mean_mean_degree",
                "t1_vabsabcabc_standard", "t1_age_years","t1_age")

# Scale only the predictors
ASD_SRS <- ASD_SRS %>%
  mutate(across(all_of(predictors), ~ as.numeric(scale(.))))
```

#SRS rolling MD
```{r}

# 1. First, order the participants by age
SRS_ordered <- ASD_SRS %>%
  arrange(age_for_filtering)

# 2. Define the sliding window parameters
window_size <- 60
step_size <- 8
total_n <- nrow(SRS_ordered)

# Calculate the absolute last possible start index
last_start_possible <- total_n - window_size + 1

# Generate indices: 1, 6, 11... 
start_indices <- seq(1, last_start_possible, by = step_size)

# FEATURE: If the step sequence missed the final index (52), add it manually
if (tail(start_indices, 1) != last_start_possible) {
  start_indices <- c(start_indices, last_start_possible)
}

results_list <- list()

# 3. The Sliding Loop (by index)
# We stop when the window can no longer fit 30 participants
for (start_idx in start_indices) {
  
  end_idx <- start_idx + window_size - 1
  
  # Extract the specific 30 participants for this bin
  bin_data <- SRS_ordered[start_idx:end_idx, ]
  
  # Check for factor level diversity (e.g., both sexes must be present)
  if (length(unique(bin_data$t1_sex)) > 1 
      # && length(unique(bin_data$t1_site)) > 1
      ) {
    
    # Run the GLM (Linear Model)
    
        m_bin <- lm(t1_srs_tscore_parent ~ PLV_6_9_DK_mean_mean_degree + t1_site + 
                t1_age_years 
                #+ 
                , 
                data = bin_data)
    
    # Extract stats for the specific predictor
    stats <- tidy(m_bin) %>% 
      filter(term == "PLV_6_9_DK_mean_mean_degree")
    
    if (nrow(stats) > 0) {
      results_list[[paste0("idx_", start_idx)]] <- data.frame(
        n_in_bin = nrow(bin_data),
        min_age = min(bin_data$age_for_filtering, na.rm = TRUE),
        max_age = max(bin_data$age_for_filtering, na.rm = TRUE),
        avg_age = mean(bin_data$age_for_filtering, na.rm = TRUE),
        beta_estimate = stats$estimate,
        std_error = stats$std.error,
        p_value = stats$p.value
        
      )
    }
  }
}

# 4. Combine into final dataframe
rolling_results_idx <- bind_rows(results_list)

rolling_results_idx <- rolling_results_idx %>%
  mutate(p_FDR = p.adjust(p_value, method = "BH"))

rolling_results_idx <- rolling_results_idx %>%
  mutate(sig_star = ifelse(p_value < 0.05, "*", ""))

#from the rolling results df, remove the second to last row
rolling_results_idx <- rolling_results_idx[- (nrow(rolling_results_idx) - 1), ]

# View the output
print(rolling_results_idx)
```


```{r}
rolling_MD = ggplot(rolling_results_idx, aes(x = avg_age, y = beta_estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  geom_line(color = "royalblue", size = 1) +
  geom_point() +
  geom_ribbon(aes(ymin = beta_estimate - std_error, 
                  ymax = beta_estimate + std_error), 
              alpha = 0.2, fill = "royalblue") +
  labs(title = "a) Effect size of MD on SRS T-score across age",
       x = "Average Age in Bin",
       y = "Estimated coefficient - MD") +
  geom_text(aes(label = sig_star, y = 1), 
            size = 8, 
            color = "black") +
  scale_x_continuous(breaks = seq(6, 32, by = 2)) +
  theme_minimal()+
    theme(aspect.ratio = 0.6,panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))

rolling_MD
```

#SRS rolling SWI
```{r}

# 1. First, order the participants by age
SRS_ordered <- ASD_SRS %>%
  arrange(age_for_filtering)

# 2. Define the sliding window parameters
window_size <- 60
step_size <- 8
total_n <- nrow(SRS_ordered)

# Calculate the absolute last possible start index
last_start_possible <- total_n - window_size + 1

# Generate indices: 1, 6, 11... 
start_indices <- seq(1, last_start_possible, by = step_size)

# FEATURE: If the step sequence missed the final index (52), add it manually
if (tail(start_indices, 1) != last_start_possible) {
  start_indices <- c(start_indices, last_start_possible)
}

results_list <- list()

# 3. The Sliding Loop (by index)
# We stop when the window can no longer fit 30 participants
for (start_idx in start_indices) {
  
  end_idx <- start_idx + window_size - 1
  
  # Extract the specific 30 participants for this bin
  bin_data <- SRS_ordered[start_idx:end_idx, ]
  
  # Check for factor level diversity (e.g., both sexes must be present)
  if (length(unique(bin_data$t1_sex)) > 1 
      # && length(unique(bin_data$t1_site)) > 1
      ) {
    
    # Run the GLM (Linear Model)
    
        m_bin <- lm(t1_srs_tscore_parent ~ PLV_6_9_DK_mean_SWI + t1_site + 
                t1_age_years 
                #+ 
                , 
                data = bin_data)
    
    # Extract stats for the specific predictor
    stats <- tidy(m_bin) %>% 
      filter(term == "PLV_6_9_DK_mean_SWI")
    
    if (nrow(stats) > 0) {
      results_list[[paste0("idx_", start_idx)]] <- data.frame(
        n_in_bin = nrow(bin_data),
        min_age = min(bin_data$age_for_filtering, na.rm = TRUE),
        max_age = max(bin_data$age_for_filtering, na.rm = TRUE),
        avg_age = mean(bin_data$age_for_filtering, na.rm = TRUE),
        beta_estimate = stats$estimate,
        std_error = stats$std.error,
        p_value = stats$p.value
        
      )
    }
  }
}

# 4. Combine into final dataframe
rolling_results_idx <- bind_rows(results_list)

rolling_results_idx <- rolling_results_idx %>%
  mutate(p_FDR = p.adjust(p_value, method = "BH"))

rolling_results_idx <- rolling_results_idx %>%
  mutate(sig_star = ifelse(p_value < 0.05, "*", ""))

#from the rolling results df, remove the second to last row
rolling_results_idx <- rolling_results_idx[- (nrow(rolling_results_idx) - 1), ]

# View the output
print(rolling_results_idx)
```


```{r}
rolling_MD = ggplot(rolling_results_idx, aes(x = avg_age, y = beta_estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  geom_line(color = "royalblue", size = 1) +
  geom_point() +
  geom_ribbon(aes(ymin = beta_estimate - std_error, 
                  ymax = beta_estimate + std_error), 
              alpha = 0.2, fill = "royalblue") +
  labs(title = "b) Effect size of SWI on SRS T-score across age",
       x = "Average Age in Bin",
       y = "Estimated coefficient - SWI") +
  geom_text(aes(label = sig_star, y = 5), 
            size = 8, 
            color = "black") +
  scale_x_continuous(breaks = seq(6, 32, by = 2)) +
  theme_minimal()+
    theme(aspect.ratio = 0.6,panel.background = element_rect(fill = "white", colour = "black"), plot.title = element_text(hjust = 0.5, size=16), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15))

rolling_MD
```
